### 2022-03-23 CV2/CV.tex
-

\section{Personal Data}

\begin{tabular}{rl}
\textsc{Email} & \href{mailto:dakovalev1@gmail.com}{dakovalev1@gmail.com}\\
\textsc{Website} & \href{https://www.dmitry-kovalev.com}{www.dmitry-kovalev.com}\\
\textsc{Phone} & +7 905 719 06 98\\
\textsc{Google Scholar} &\href{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}{https://scholar.google.com/citations?user=qHFA5z4AAAAJ}
\end{tabular}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabular}{rl}	
\textsc{2014-2018}& BS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\textsc{2018-2019}& MS in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\textsc{2018-2021}& MS in Applied Mathematics and Physics\\
& \textbf{Moscow Institute of Physics and Technology}, Dolgoprudny, Russia\\
& Advisor: \href{https://scholar.google.com/citations?user=AmeE8qkAAAAJ}{Alexander Gasnikov}\\
\textsc{2019-Now}& PhD in Computer Science\\
& \textbf{King Abdullah University of Science and Technology}, Thuwal, Saudi Arabia\\
& Advisor: \href{https://richtarik.org}{Peter Richt\'{a}rik}\\
\end{tabular}

\section{Research Interests}
 Optimization Algorithms, Distributed Optimization, Machine Learning,

\section{Skills}

\begin{tabular}{rl}
	\textsc{Programming} & C/C++, Python; \textsc{Past experience:} Go, C\#, VB.NET\\
	\textsc{Computer} & macOS, LaTeX, Git\\
	\textsc{Mathematics} & Calculus, Linear Algebra, Probability and Statistics, Convex Analysis\\
\end{tabular}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\section{Languages}

\begin{tabular}{rl}
\textsc{English} & Advanced Knowledge \\
\textsc{Russian} & Mothertongue\\
\end{tabular}

\section{Awards}
\hypersetup{colorlinks,breaklinks,urlcolor=black,linkcolor=black}
\begin{tabular}{cl}
	\textsc{2021} & \textbf{CEMSE Research Excellence Award}, King Abdullah University of Science and Technology\\
	\textsc{2021} & \href{http://federated-learning.org/fl-icml-2021/}{\textbf{Best Student Paper Award}, FL-ICML 2021 Workshop}\\
	\textsc{2021} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex} \\
	\textsc{2020} & \href{https://yandex.ru/scholarships/scholars}{\textbf{Ilya Segalovich Scientific Prize}, Yandex}\\
	\textsc{2015-2017} & \textbf{Abramov’s Fund Scholarship}, Moscow Institute of Physics and Technology\\
	\textsc{2014} & \textbf{Asian Physics Olympiad (APhO), Honourable Mention}, Singapore\\
	\textsc{2014} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saint-Petersburg\\
	\textsc{2014} & \textbf{All-Russian School Programming Olympiad, Region Round Winner}, Moscow\\
	\textsc{2014} & \textbf{All-Russian School Math Olympiad, Region Round Winner}, Moscow\\
	\textsc{2012-2014} & \textbf{Russian President’s Scholarship for High School Sudents}\\
	\textsc{2012-2014} & \textbf{Moscow Governor’s Scholarship for High School Sudents}\\
	\textsc{2013} & \textbf{All-Russian School Physics Olympiad, Final Round Winner}, Vladivostok\\
	\textsc{2012} & \textbf{All-Russian School Physics Olympiad, Final Round Prize-Winner}, Saransk\\
\end{tabular}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\newpage

\section{Papers}

@@

>>>>

\input{general}

@@

\input{date.tex}
